---
title: "Allergy Dashboard 1"
output: 
  flexdashboard::flex_dashboard:
    theme: flatly
    orientation: rows
    vertical_layout: fill
    css: custom.css  # Include custom CSS file

---

 

```{r, include=FALSE, warnings=FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```


```{r setup, include=FALSE}
 
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(ggalluvial)
library(ggsankey)
library(stringr)
library(flexdashboard)
library(ggplot2)
library(dplyr)
library(knitr)
library(DT)
library(rpivotTable)
library(plotly)
library(highcharter)
library(reactable)
library(bslib)
library(bsicons)
library(shiny)
library(networkD3)
library(kableExtra)

```

```{r, include=FALSE, warnings=FALSE, message=FALSE}
 
  
```

```{r}
colors<-c("#1b9e77","#d95f02","#e7298a","#7570b3","#a6761d")
```

# Skin Prick Test Overview

row
------------------------------


### Total Number of Patients Who Underwent Skin Prick Testing

```{r}
valueBox(paste("Total  2549"),
         color = "black")
```

### Number of Patients Who Tested Positive in the Skin Prick Test

```{r}
valueBox(paste("Positive  1915 (75.13%)"),
         color = "#e41a1c")
```

## row  
-----------------------------------------------------------------------
 

### Gender Distribution of Positive Cases {data-width=300}


```{r}
# Load the dataset
data <- read.csv("Skin_Test_Data_Positive_Cases.csv")

# Convert all gender values to uppercase to standardize
data$Gender <- toupper(data$Gender)

# Recode F to FEMALE, M to MALE
data$Gender[data$Gender == "F"] <- "FEMALE"
data$Gender[data$Gender == "M"] <- "MALE"

# Keep only rows with Gender as MALE or FEMALE
data <- subset(data, Gender %in% c("MALE", "FEMALE"))

# Compute gender counts and percentages
gender_table <- table(data$Gender)  # Get counts
gender_counts <- as.vector(gender_table)  # Convert to numeric
gender_percentages <- prop.table(gender_table) * 100  # Compute percentages
Percentage = round(gender_percentages, 2) # Round percentages

# Create a dataframe
gender_data <- data.frame(
  Gender = names(gender_table),
  Count = gender_counts,
  Percentage = Percentage
)

# Manually modify the gender labels to have only the first letter capitalized
gender_data$Gender <- ifelse(gender_data$Gender == "MALE", "Male", 
                             ifelse(gender_data$Gender == "FEMALE", "Female", gender_data$Gender))

# Plot bar chart
p1 <- ggplot(gender_data, aes(x = Gender, y = Percentage, fill = Gender, 
                              text = paste0("Gender: ", Gender, 
                                            "<br>Count: ", Count,  
                                            "<br>Percentage: ", Percentage, "%"))) +
  geom_bar(stat = "identity", color = "black", width = 0.4, size = 0.2) +  # Reduce bar width
  scale_fill_manual(values = c("#a6cee3", "#1f78b4")) +
  labs(x = "Gender", y = "Percentage", title = "Gender Distribution") +
  ylim(0, 100) +
  theme_minimal()

# Convert to interactive plot
ggplotly(p1, tooltip = "text")


```   

### Age Distribution of Positive Cases{data-width=300}
    
```{r}
# Ensure Age is numeric and remove missing values
data$Age <- as.numeric(data$Age)
data <- data[!is.na(data$Age), ]

# Create histogram
p2 <- ggplot(data, aes(x = Age)) +
  geom_histogram(binwidth = 5, fill = "#33a02c", color = "black", alpha = 0.7, size = 0.2) +
  labs(x = "Age", y = "Count", title = "Age Distribution") +
  theme_minimal()

# Convert to interactive plot
plotly::ggplotly(p2)


```

### Age Group Distribution of Positive Cases{data-width=400}
    
```{r}
# Remove rows with NA in Age
df <- data %>%
  filter(!is.na(Age)) %>%
  mutate(Age_group = case_when(
    Age <= 1                     ~ "Infant",       # 1 year and below
    Age > 1 & Age < 12           ~ "Child",        # 2 - 11 years
    Age >= 12 & Age < 18         ~ "Adolescent",   # 12 - 17 years
    Age >= 18 & Age < 65         ~ "Adult",        # 18 - 64 years
    Age >= 65                    ~ "Elderly"       # 65+ years
  ))

# Count the number of individuals in each Age Group
age_group_counts <- df %>%
  group_by(Age_group) %>%
  summarise(Count = n(), .groups = "drop") %>%
  arrange(desc(Count))

# Calculate total and percentages
total_count <- sum(age_group_counts$Count)

age_group_counts <- age_group_counts %>%
  mutate(Percentage = Count / total_count * 100)

# Set factor levels to control bar order
age_group_counts$Age_group <- factor(age_group_counts$Age_group, 
                                     levels = c("Infant", "Child", "Adolescent", "Adult", "Elderly"))

# Create bar plot
P4 <- ggplot(age_group_counts, aes(x = Age_group, y = Count, fill = Age_group,
                                   text = paste("Age Group:", Age_group,
                                                "<br>Count:", Count,
                                                "<br>Percentage:", round(Percentage, 1), "%"))) +
  geom_bar(stat = "identity", color = "black", width = 0.8, size = 0.2) +
  labs(x = "Age Group", y = "Count", title = "Age Group Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 10),
        legend.key.size = unit(0.5, "cm")) +
  scale_fill_manual(values = c("Infant" = "#1b9e77", "Child" = "#d95f02",
                               "Adolescent" = "#7570b3", "Adult" = "#e6ab02", "Elderly" = "#a6761d")) +
  guides(fill = guide_legend(title = "Age Group"))

# Make interactive with plotly
plotly::ggplotly(P4, tooltip = "text")
 

```






Allergens
==============================

row
------------------------------

### Common Allergens

```{r}
valueBox(paste("18"),
         color = "black")
```

### Common Food Allergens

```{r}
valueBox(paste("10"),
         color = "#1b9e77")
```

### Common Aero Allergens

```{r}
valueBox(paste("8"),
         color = "#d95f02")
```
 
 
 
## Chart B {.tabset}

### Aero Allergen Combinations  

```{r}
# Define the data
allergen_names <- c("House dust mite", "Cockroach", "Mould mite", "Dog hair", "Prawns/Shrimp", 
                    "Aspergillus fumigatus", "Cat", "Cows milk", "Wheat flour", "Beef", 
                    "Weed mix", "Pork", "Mutton", "Gelatin", "Grass", "Egg", "Tuna", "Coconut","Other")

test_numbers <- c(9, 17, 45, 8, 18, 3, 7, 5, 23, 4, 171, 15, 38, 114, 119, 10, 21, 24,200)

# Create a mapping between test numbers and allergen names
allergen_mapping <- setNames(allergen_names, test_numbers)

# Define the table
table <- data.frame(
  Number = 1:31,
  Combination = c( "9", "9, 17", "9, 17, 45", "9, 45", "18", 
                  "8, 9", "3, 9, 17", "8, 9, 17", "7, 8, 9, 17", "4", 
                  "5", "17", "23", "7, 9, 17", "9, 18", "10", "21", 
                  "3", "3, 7, 8, 9, 17", "114", "24", "3, 7, 8, 9, 17, 119, 171", 
                  "3, 8, 9, 17", "3, 9", "4, 15, 38, 114", "7, 9", "7, 8, 9", 
                  "9, 17, 171", "45", "8, 9, 45","200"),
  Count = c(237, 150, 44, 36, 34, 32, 30, 27, 25, 24, 23, 22, 22, 
            21, 21, 20, 16, 16, 16, 14, 14, 13, 13, 13, 13, 13, 12, 12, 
            11, 11,960),
  Percentage_Count = c(12.38, 7.83, 2.30, 1.88, 1.78, 1.67, 1.57, 
                       1.41, 1.31, 1.25, 1.20, 1.15, 1.15, 1.10, 1.10, 1.04, 
                       0.84, 0.84, 0.84, 0.73, 0.73, 0.68, 0.68, 0.68, 0.68, 
                       0.68, 0.63, 0.63, 0.57, 0.57,50.13)
)

#Function to map test numbers to allergen names
map_to_allergen_names <- function(Combination) {
  # Split the combination string into individual test numbers
  test_nums <- as.numeric(unlist(strsplit(Combination, ", ")))
  
  # Map test numbers to allergen names
  allergen_names <- sapply(test_nums, function(num) allergen_mapping[as.character(num)], USE.NAMES = FALSE)
  
  # Combine allergen names into a single string
  paste(allergen_names, collapse = ", ")
}

# Apply the function to complete the Combination_Name column
table$Combination_Name <- sapply(table$Combination, map_to_allergen_names)


# Function to determine the type of allergy (Food, Aero, or Aero/Food)
determine_allergy_type <- function(Combination_Name) {
  # Check if the combination contains "Other"
  if (grepl("Other", Combination_Name)) {
    return("Aero/Food")
  }
  
  # Check if the combination contains any Food allergens
  has_food <- any(grepl("Prawns/Shrimp|Cows milk|Wheat flour|Beef|Pork|Mutton|Gelatin|Egg|Tuna|Coconut", Combination_Name))
  
  # Check if the combination contains any Aero allergens
  has_aero <- any(grepl("House dust mite|Cockroach|Mould mite|Dog hair|Aspergillus fumigatus|Cat|Weed mix|Grass", Combination_Name))
  
  # Determine the type of allergy
  if (has_food && has_aero) {
    return("Aero/Food")
  } else if (has_food) {
    return("Food")
  } else {
    return("Aero")
  }
}

# Apply the function to determine the type of allergy
table$Allergen_Type <- sapply(table$Combination_Name, determine_allergy_type)
# Define colors for each allergen type
allergen_colors <- c("Aero" = "#d95f02", "Food" = "#1b9e77", "Aero/Food" = "#7570b3")

# Create the bar plot using ggplot
p <- ggplot(table, aes(x = as.factor(Number), y = Percentage_Count, fill = Allergen_Type, text = Combination_Name)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = allergen_colors) + 
  labs(title = "Percentage Count of Allergen Combination",
       x = "Combination Number",
       y = "Percentage Count (%)",
       fill = "Allergen Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

# Define colors for each allergen type
allergen_colors <- c("Aero" = "#d95f02", "Food" = "#1b9e77")

# Filter data for Aero allergens
aero_table <- subset(table, Allergen_Type == "Aero")

# Filter data for Food allergens
food_table <- subset(table, Allergen_Type == "Food")
# Create the Aero allergens bar plot
aero_plot <- ggplot(aero_table, aes(x = as.factor(Number), y = Percentage_Count, fill = Allergen_Type, text = Combination_Name)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = allergen_colors) + 
  labs(title = "Percentage Count of Aero Allergens",
       x = "Combination Number",
       y = "Percentage Count (%)",
       fill = "Allergen Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.4, hjust=1))

# Convert Aero ggplot to interactive plotly
aero_plotly <- ggplotly(aero_plot, tooltip = "text")
# Create the Food allergens bar plot
food_plot <- ggplot(food_table, aes(x = as.factor(Number), y = Percentage_Count, fill = Allergen_Type, text = Combination_Name)) +
  geom_bar(stat = "identity" ,width = 0.4, linewidth = 0.15) +
  scale_fill_manual(values = allergen_colors) + 
  labs(title = "Percentage Count of Food Allergens",
       x = "Combination Number",
       y = "Percentage Count (%)",
       fill = "Allergen Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.4, hjust=1))

# Convert Food ggplot to interactive plotly
food_plotly <- ggplotly(food_plot, tooltip = "text")
# Display plots
aero_plotly

```

### Food Allergen Combinations {data-width=600}

```{r}
food_plotly
```

 
### Aero and Food Allergen Combinations {data-width=400}

```{r}
ggplotly(p, tooltip = "text")
```


Data Table
============================


```{r}
# Load necessary library
library(DT)

# Define the data
allergen_names <- c("House dust mite", "Cockroach", "Mould mite", "Dog hair", "Prawns/Shrimp", 
                    "Aspergillus fumigatus", "Cat", "Cows milk", "Wheat flour", "Beef", 
                    "Weed mix", "Pork", "Mutton", "Gelatin", "Grass", "Egg", "Tuna", "Coconut", "Other")

test_numbers <- c(9, 17, 45, 8, 18, 3, 7, 5, 23, 4, 171, 15, 38, 114, 119, 10, 21, 24, 200)

# Create a mapping between test numbers and allergen names
allergen_mapping <- setNames(allergen_names, test_numbers)

# Define the table
table <- data.frame(
  Number = 1:31,
  Combination = c( "9", "9, 17", "9, 17, 45", "9, 45", "18", 
                   "8, 9", "3, 9, 17", "8, 9, 17", "7, 8, 9, 17", "4", 
                   "5", "17", "23", "7, 9, 17", "9, 18", "10", "21", 
                   "3", "3, 7, 8, 9, 17", "114", "24", "3, 7, 8, 9, 17, 119, 171", 
                   "3, 8, 9, 17", "3, 9", "4, 15, 38, 114", "7, 9", "7, 8, 9", 
                   "9, 17, 171", "45", "8, 9, 45", "200"),
  Count = c(237, 150, 44, 36, 34, 32, 30, 27, 25, 24, 23, 22, 22, 
            21, 21, 20, 16, 16, 16, 14, 14, 13, 13, 13, 13, 13, 12, 12, 
            11, 11, 960),
  Percentage_Count = c(12.38, 7.83, 2.30, 1.88, 1.78, 1.67, 1.57, 
                       1.41, 1.31, 1.25, 1.20, 1.15, 1.15, 1.10, 1.10, 1.04, 
                       0.84, 0.84, 0.84, 0.73, 0.73, 0.68, 0.68, 0.68, 0.68, 
                       0.68, 0.63, 0.63, 0.57, 0.57, 50.13)
)

# Function to map test numbers to allergen names
map_to_allergen_names <- function(Combination) {
  # Split the combination string into individual test numbers
  test_nums <- as.numeric(unlist(strsplit(Combination, ", ")))
  
  # Map test numbers to allergen names
  allergen_names <- sapply(test_nums, function(num) allergen_mapping[as.character(num)], USE.NAMES = FALSE)
  
  # Combine allergen names into a single string
  paste(allergen_names, collapse = ", ")
}

# Apply the function to complete the Combination_Name column
table$Combination_Name <- sapply(table$Combination, map_to_allergen_names)

# Function to determine the type of allergy (Food, Aero, or Aero/Food)
determine_allergy_type <- function(Combination_Name) {
  # Check if the combination contains "Other"
  if (grepl("Other", Combination_Name)) {
    return("Aero/Food")
  }
  
  # Check if the combination contains any Food allergens
  has_food <- any(grepl("Prawns/Shrimp|Cows milk|Wheat flour|Beef|Pork|Mutton|Gelatin|Egg|Tuna|Coconut", Combination_Name))
  
  # Check if the combination contains any Aero allergens
  has_aero <- any(grepl("House dust mite|Cockroach|Mould mite|Dog hair|Aspergillus fumigatus|Cat|Weed mix|Grass", Combination_Name))
  
  # Determine the type of allergy
  if (has_food && has_aero) {
    return("Aero/Food")
  } else if (has_food) {
    return("Food")
  } else {
    return("Aero")
  }
}

# Apply the function to determine the type of allergy
table$Allergen_Type <- sapply(table$Combination_Name, determine_allergy_type)

# Select the relevant columns (excluding 'Number')
table_selected_columns <- table[, c("Number","Combination","Combination_Name", "Count", "Percentage_Count", "Allergen_Type")]

# Replace underscores with spaces in column names
colnames(table_selected_columns) <- gsub("_", " ", colnames(table_selected_columns))

# Print the updated table using datatable
datatable(table_selected_columns,
          caption = "Common Allergen Combinations",
          rownames = FALSE,
          filter = "top",
          options = list(pageLength = 10)
)

```

Sankey Diagram
============================

### Sankey Diagram

```{r}
 # Load necessary libraries
library(tidyverse)
library(networkD3)

# Load the dataset
data <- read_csv("D:/MSc Research/Allergy_data/table.csv")

# Remove rows where Combination_Name is "Other"
data <- data %>% filter(Combination_Name != "Other")  # Fixed the filtering issue

# Convert to long format for Sankey diagram
df_long <- data %>% select(Allergen_Type, Combination_Name)

# Create a unique node list
nodes <- data.frame(name = unique(c(df_long$Allergen_Type, df_long$Combination_Name)))

# Identify right-side (Combination_Name) nodes for gray color
right_nodes <- df_long$Combination_Name

# Assign colors: left-side nodes colored, right-side nodes gray
nodes$group <- ifelse(nodes$name %in% right_nodes, "Gray",  # Right-side nodes (Combination_Name) -> Gray
               ifelse(grepl("Aero/Food", nodes$name), "Aero/Food",
               ifelse(grepl("Aero", nodes$name), "Aero",
               ifelse(grepl("Food", nodes$name), "Food", "Other"))))

# Map source and target to node index
df_long <- df_long %>%
  mutate(source = match(Allergen_Type, nodes$name) - 1,
         target = match(Combination_Name, nodes$name) - 1,
         value = 1)  # Assigning a weight of 1 for equal connections

# Assign link color based on the left-side source node
df_long$group <- nodes$group[df_long$source + 1]  # Ensure correct indexing

# Define JavaScript color scale
color_scale <- 'd3.scaleOrdinal()
  .domain(["Aero", "Food", "Aero/Food", "Gray"])
  .range(["#d95f02", "#1b9e77", "#7570b3", "gray"])'  # Aero/Food is purple

# Create Sankey diagram with correct colors
sankey <- sankeyNetwork(Links = df_long, Nodes = nodes,
                        Source = "source", Target = "target",
                        Value = "value", NodeID = "name",
                        fontSize = 20, nodeWidth = 35,
                        NodeGroup = "group", colourScale = color_scale,width = 1400, height = 600,
                        LinkGroup = "group")  # Keeps links colored by left node

# Display the Sankey diagram
sankey


```

# Heat Map

### Heat Map

 
```{r}
#Read the CSV file with the correct file path and store it in a properly named variable
df_combination_frequency_CSV <- read.csv("D:/MSc Research/Allergy_data/df_combination_frequecy_CSV.csv", row.names=1)

# View the dataset (assuming you meant to view the CSV data)
df_combination_frequency_CSV<-data.matrix(df_combination_frequency_CSV) 

heatmap(df_combination_frequency_CSV)


```

